Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-03-15 endofquarterpaper.qmd
editing up to results: Cultural Group Strength

Network analysis shows similar groups to the ones identified in @fig-seriation, but it also shows evolving inter-connectivity between groups. In the Transitional phase, the network analysis shows two clearly defined groups, one consisting of Geissenklösterle, Fumane, and Pod Hradem, and the other consisting of Hohle Fels, El Castillo, and Labeko Koba, with no connections between the groups. The Proto-Aurignacian phase also shows two clearly defined groups, one consisting of Geissenklösterle, Spy, Vogelherd, and Grotte du Renne, and the other consisting of Mladeč, Hohlenstein-Stadel, Gatzarria, and Abri Pataud. However, it also displays some sites that are less clearly connected, with La Ferrassie being squarely in between both groups with equal connections to both, and Les Cottés lacking a connection to any of the groups. The Early Aurignacian shows more strongly inter-connected groups - although the shape still suggests two main groups - with Grotte de la Verpillière I in particular having multiple strong connections to both of the groups. Lastly, the Evolved Aurignacian again shows two main groups, although group inner-connectivity has decreased, one consisting of Hohle Fels, Trou Magrite, Vogelherd, and Bockstein-Törle, and the other consisting of Gargas, La Viña, Sirgenstein Cave, Vindija Cave, and Les Rois. While inter-connectivity between groups is still present, with connections between Trou Magrite, Gargas, and Vindija Cave, and Bockstein-Törle and Gargas, the strength of inter-connectivity is weaker than in the Early Aurignacian.

In identifying the groups, we referenced both the seriation and network analyses. The results of the above tests allowed us to find two main groups of sites within each phase, as shown in @tbl-group-table. The geographic distributions of the groups are shown in @fig-group-map, and the sign makeup of each group is shown in @fig-group-sign.

```{r}
#| label: tbl-group-table
#| tbl-cap: "Table of the sites by group per phase"
#| tbl-cap-location: bottom
group_table <- read_excel("data/site-groups.xlsx")

kable(group_table)

@@

>>>>

The results of the network analysis supports the restricted-broad groupings identified in @fig-seriation, and provides additional insights into the evolution of connectivity between groups. In the Transitional phase, the network analysis reveals two distinct and disconnected groups. The restricted group consists of Geissenklösterle, Fumane, and Pod Hradem, and the broad group consisting of Hohle Fels, El Castillo, and Labeko Koba, with no connections between the groups. The Proto-Aurignacian phase also shows two clearly defined groups, the broad group consisting of Geissenklösterle, Spy, Vogelherd, and Grotte du Renne, and the restricted group consisting of Mladeč, Hohlenstein-Stadel, Gatzarria, and Abri Pataud. However, it also displays some connectivity between the two groups of sites, with La Ferrassie connected to both groups. Les Cottés stands out with no connections to either group. The Early Aurignacian shows more strongly inter-connected groups -- although the shape still suggests two main groups -- with Grotte de la Verpillière I in particular having multiple strong connections to both groups. Lastly, the Evolved Aurignacian again shows two main groups, although intra-group connectivity has decreased, with the broad group consisting of Hohle Fels, Trou Magrite, Vogelherd, and Bockstein-Törle, and the restricted group consisting of Gargas, La Viña, Sirgenstein Cave, Vindija Cave, and Les Rois. As for the Early Aurignacian,inter-connectivity between groups continues to be evident in the Evolved Aurignacian, with connections between Trou Magrite, Gargas, and Vindija Cave, and Bockstein-Törle and Gargas, however the strength of inter-connectivity is weaker than in the Early Aurignacian.

@@

<!-- BM: I reckon here might be the place to make some comments about geographic distribution of the groups and boundaries, and reference the map below -->
